Summary of consumption in Medicare Part D

### 2017-01-20 hicks-summary/melt/summary-doc.Rmd
added temporal commentary

---
title: "Summary of consumption in Medicare Part D"
author: "Scott Olesen"
date: "1/19/2017"
bibliography: "refs.bib"
output: html_document
---

@@

@@

```{r, echo=FALSE}
dat %>%
  filter(type=='top_abx_rx') %>%
  select(-type) %>% 
  spread(year, rx) %>%
  arrange(desc(`2011`)) %>%
  rename(antibiotic=field) %>%
  kable
```

@@

Our result, that the consumption of antibiotics by women and men is in a 3:2 ratio, agrees with the result in @hicks-us-2015.

@@

@@

When stratifying by age, @hicks-us-2015 places all people 65 or older into one stratum. Here I stratify within this population. Excepting the beneficiaries under 65, older beneficiaries tend to consume more antibiotics. The beneficiaries under 65 qualify for Medicare because they are disabled, have end stage renal disease, or ALS, which might contribute to their increased consumption of antibiotics.

>>>>

---
title: "Summary of consumption in Medicare Part D"
author: "Scott Olesen"
date: "1/19/2017"
output: html_document
bibliography: refs.bib
---

@@

Across years, the consumption of drugs seems to follow similar patterns (excepting that consumption in 2012 was about 20% higher than in 2011 and consumption in 2013-2014 was about 10% higher).

All consumption rates are reported as PKPY.

@@

Allowing for the overall differences in consumption, consumption of azithromycin appears to have declined during 2011 to 2014, while the consumption of levofloxacin increased.

```{r top_abx, echo=FALSE}
dat %>%
  filter(type=='top_abx_rx') %>%
  select(-type) %>% 
  spread(year, rx) %>%
  arrange(desc(`2011`)) %>%
  rename(antibiotic=field) %>%
  kable
```

@@

Our result, that the consumption of antibiotics by women and men is in a 3:2 ratio, agrees with the result in @hicks-us-2015. The ratio also remained steady across years in our dataset.

@@

In @hicks-us-2015, stratifying consumption in 2011 by census region led to one major divide: the South, West, and Northeast consumed more antibiotics than the West (931, 897, and 848 vs. 647 PKPY). In our results, the major divide is between the South and the Midwest, West, and Northeast (641 vs. 583, 563, and 533 PKPY).

In our data, 2012 appears exceptional: consumption in the Midwest and West was relatively high, and consumption in the Northeast was relatively low. Results from 2013 and 2014 accord more closely with the results from @hicks-us-2015, in which the West is the region with the lowest consumption.

@@

When stratifying by age, @hicks-us-2015 places all people 65 or older into one stratum. Here I stratify within this population. Excepting the beneficiaries under 65, older beneficiaries tend to consume more antibiotics. The beneficiaries under 65 qualify for Medicare because they are disabled, have end stage renal disease, or ALS, which might contribute to their increased consumption of antibiotics. However, this trend across age groups does not hold in 2012.
